Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-08-15 article.tex
Nick's comments
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1349 ccdd05d5-56c1-461a-bf98-85f6876523b4

During testing, we were surprised that careful design of the decimation and
interpolation stages made a crucial difference in terms of computational
overhead.  Connecting the interpolation filters in cascade fashion rather than
in parallel made a significant difference.  Also, between $N^\shortuparrow = 16$
and $N^\shortuparrow = 192$ the total cost in \flops\ varied across an order of
magnitude.  There is possibly further room for optimization beyond minimizing
$N^\shortuparrow$.  We have considered designing our own custom decimation and
interpolation filters or tuning these filters separately for each time slice.
We now appreciate that the efficiency of \lloid\ hinges on proper specification
of $N^\shortuparrow$.

>>>>

We found that careful design of the decimation and interpolation stages made a
crucial difference in terms of computational overhead.  Connecting the
interpolation filters in cascade fashion rather than in parallel made a
significant difference.  Also, between $N^\shortuparrow = 16$ and
$N^\shortuparrow = 192$ the total cost in \flops\ varied across an order of
magnitude.  We now appreciate that the efficiency of \lloid\ hinges on proper
specification of $N^\shortuparrow$.
